---
title: "Lab 07 - Modelling course evaluations"
author: [Squirrels]
output: 
  tufte::tufte_html:
    css: ../lab.css
    tufte_variant: "envisioned"
    highlight: pygments
link-citations: yes

---

### Load packages 

```{r load-packages, message=FALSE}
library(tidyverse)
library(tidymodels)
library(patchwork)
```

### Read in data

```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```


### Exercise 1

```{r viz-score}
evals %>%
  ggplot() +
  geom_histogram(aes(x = score))
```

The graph is clearly left-skewed! This means that students are giving higher than average ratings most of the time. You would expect to see a bell curve over the average. This tells us students are rating courses based on external factors.

### Exercise 2

```{r viz-score-bty, eval = FALSE}
plot_geom_point  <- ggplot(evals) +
  geom_point(aes(x = score, y = bty_avg))

plot_geom_jitter <- ggplot(evals) +
  geom_jitter(aes(x = score, y = bty_avg))

plot_geom_point + plot_geom_jitter
```

Jitter adds some random variation to the location of each point. In the first plot some points are overlapping.

### Exercise 3

```{r fit-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(___ ~ ___, data = ___)
```

```{r tidy-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
tidy(___)
```

*Add your linear model here. Don't worry too much about notation, you can use things like score-hat.*

### Exercise 4

```{r viz-score_bty_fit}
# add your code here
```

### Exercise 5

*Add interpretation of intercept here.*

### Exercise 6

*Add interpretation of intercept here.*

### Exercise 7

```{r glance-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)
```

*Add interpretation of R-squared here.*

### Exercise 8

```{r viz-score_bty_fit-diagnostic, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

ggplot(___)
```

*Add your narrative here.*

### Exercise 9

```{r fit-score_rank_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

### Exercise 10

```{r fit-score_gender_fit}
# fit model

# tidy model output
```

```{r score_gender_intercept, echo = FALSE, eval = FALSE}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope, echo = FALSE, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "___") %>%
  select(___) %>%
  pull()
```

*Add your narrative here.*

### Exercise 11

```{r fit-score_bty_gender_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

### Exercise 12

```{r glance-score_bty_gender_fit}
# glance model output
```

*Add your narrative here.*

### Exercise 13

*Add your linear model here. Don't worry about math notation, you can use things like score-hat.*

### Exercise 14

*Add your narrative here. One sentence is sufficient.*

### Exercise 15

*Add your narrative here. One sentence is sufficient.*

### Exercise 16

*Add your narrative here. One sentence is sufficient.*

### Exercise 17

*Add your narrative here. One sentence is sufficient.*

### Exercise 18

```{r fit-score_bty_gender_rank_fit}
# fit model

# glance model output
```

*Add your narrative here. One sentence is sufficient.*
